What is happening on Twitter? A framework for student research projects with tweets

### 2020-08-25 Rmd/jse-special-issue-2020-october.Rmd
added latent Dirichlet allocation ref (blei 2003) to first occurence of LDA

To illustrate the value of Twitter data, we present below a 
reproducible case study. In it, we aim to detect a social media 
event by examining topic content over time. We use latent Dirichlet 
allocation models to infer topics on three consecutive days centered 
on Memorial Day 2020. We chose this example case study, 
instead of the student projects, because of limited data 
availability for the student projects. Despite this, the case study 
illustrates the strategy and methods for one of the student 
projects.

@@

Our analyses use three fields from each tweet: date ("created_at"), tweet identifier 
("id_str"), and tweet text ("text"). The "created_at" field is a character string containing 
the date and time of the tweet. Every tweet has a unique identifier, the "id_str" value. The 
"text" field contains the unicode representation of the message. After creating a text file 
with tweet JSON, our next step involved reading and parsing tweets with the R 
packages `rtweet` and `tidytext`.

@@

The next task is to wrangle the tweet JSON into a data structure suitable for latent Dirichlet allocation modeling. 
We used functions from the `rtweet` R package to parse tweet JSON into a data frame [@rtweet-package]. 
We then divided tweet text into words with functions from the `tidytext` R package [@tidytext]. We 
discarded commonly used "stop words" and emojis.

>>>>

To illustrate the value of Twitter data, we present below a 
reproducible case study. In it, we aim to detect a social media 
event by examining topic content over time. We use latent Dirichlet 
allocation models [@blei2003latent] to infer topics on three consecutive days centered 
on Memorial Day 2020. We chose this example case study, 
instead of the student projects, because of limited data 
availability for the student projects. Despite this, the case study 
illustrates the strategy and methods for one of the student 
projects.

@@

Our analyses use three fields from each tweet: date ("created_at"), tweet identifier 
("id_str"), and tweet text ("text"). The "created_at" field is a character string containing 
the date and time of the tweet. Every tweet has a unique identifier, the "id_str" value. The 
"text" field contains the unicode representation of the message. After creating a text file 
with tweet JSON, our next step involved reading and parsing tweets with the R 
packages `rtweet` [@rtweet-package] and `tidytext` [@tidytext].

@@

The next task is to wrangle the tweet JSON into a data structure suitable for latent Dirichlet allocation modeling. 
We used functions from the `rtweet` R package to parse tweet JSON into a data frame. 
We then divided tweet text into words with functions from the `tidytext` R package. We 
discarded commonly used "stop words" and emojis.
